Tree size, (microhabitat)?, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-08-15 manuscript/climate_sensitivity_draft.Rmd
updating ms (added Table5 placeholder)

@@

@@

![Table 4 (example!)](tables_figures/Table4.png) #this is tested_traits_all

>>>>

Comparing across droughts, resistance *was highest in 1964-66 drought*, lower in 1999, and lowest in 1977 (Tables 4-5).

@@

![Table 4 - individual variable tests](tables_figures/Table4.png) #this is tested_traits_all

![Table 5 - best full models ](tables_figures/Table5.png)

@@
